---
title: "Linear Model with prediction"
author: "Diana Reyes"
date: "11/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Introduction

This is the linear model with prediction problem. Predict strength scores using data from the following web site.

```{r}
dataF <- read.csv(file="http://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
```

```{r}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)
require(ggplot2)
```
## Scatterplot

```{r}
plot(SIMS~ARM,data=dataF)
```


```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=ARM))
basicNN + geom_point()+geom_smooth(method=lm)
```

## now add the model fit to plot

###Model.1

```{r}
model.1 <- lm(SIMS~ARM,data=dataF)
summary.lm(model.1)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,New,interval = "prediction")
```

Model.1 shows that the Adjusted R-Squared: 0.467 


```{r}
plot(SIMS~GRIP,data=dataF)
```

```{r}
basicNN <- ggplot(dataF,aes(y=SIMS,x=GRIP))
basicNN + geom_point()+geom_smooth(method=lm)
```
###Model.2

```{r}
model.2 <- lm(SIMS~GRIP,data=dataF)
summary.lm(model.2)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,New,interval = "prediction")
```

Model.2 reflects an Adjusted R-Squared: 0.4053 which is lower than Model.1 Adjusted R-Squared, therefore we cannot use Model.2. for variable of grip.

###Model.3

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=dataF)
summary.lm(model.3)
New=data.frame(GRIP=94,ARM=88)
predict.lm(model.3,New,interval = "prediction")
```

Model.3 reflects and Adjusted R-Squared: 0.5358 in which is higher than both Model.1 and Model.2. Model.3 will be the best model when using the variables grip and arm strength. 

##Compare Model.1 and Model.3

```{r}
anova(model.1,model.3)
```


Model.1 and Model.3 allows us to make a prediction between arm and arm plus grip in order to determine strength. 

## Conclusion

Arms and Arms plus Grips are  the best variables used in order to provide the most accurate linear models and regressions. 

